\documentclass[a4paper, 11pt]{ltjsarticle}
% --- 基本設定 ---
% \usepackage{luatexja-fontspec} % lualatexで日本語フォント指定
% Macのヒラギノフォントを指定 (存在しない場合は他のフォントに変更してください)
% \setmainjfont[BoldFont={Hiragino Sans W6}, ItalicFont={Hiragino Mincho ProN W3}]{Hiragino Sans W3}
% \setsansjfont[BoldFont={Hiragino Sans W6}]{Hiragino Sans W3}
% \setmonojfont{Osaka－等幅} % Osakaフォントがない場合は他の等幅フォントを指定

% \usepackage[haranoaji]{luatexja-preset} % Harano Aji Fonts (Noto Fonts 由来) を使う場合
\usepackage[hiragino-pro,deluxe]{luatexja-preset} % ヒラギノフォントを使う場合 (より詳細な設定)

% \usepackage[T1]{fontenc} % LuaLaTeX + fontspecでは通常不要
\usepackage{amsmath, amssymb, mathtools, amsthm} % 数式関連
\usepackage{graphicx} % 画像挿入
\usepackage{hyperref} % ハイパーリンク
\usepackage{listings} % ソースコード表示
\usepackage{enumitem} % リスト環境のカスタマイズ
\usepackage{graphicx}
\usepackage{mathrsfs}
\usepackage{romanbar}

% --- Beamerテーマと配色 (記事形式では不要なため削除・コメントアウト) ---
% \usetheme{Madrid}
% \usecolortheme{default}

% カスタムカラー (tcolorboxなどで使用するため残す)
% \definecolor{myblue}{RGB}{0,110,180}
% \definecolor{mygreen}{RGB}{0,150,100}
% \definecolor{myorange}{RGB}{230,120,20}
% \definecolor{mygray}{RGB}{240,240,240}

% Beamerの配色を一部上書き (記事形式では不要なため削除・コメントアウト)
% \setbeamercolor{palette primary}{bg=myblue,fg=white}
% ... (他のsetbeamercolorも同様に削除) ...
% \setbeamercolor{block body}{bg=mygray}

% --- tcolorboxの設定 (スタイリッシュな囲み) ---
\usepackage[most]{tcolorbox}

%================================================================
% 定理・定義・命題などのカスタムボックス環境
%================================================================

% --- 必要なパッケージ（プリアンブルにあることを確認）---
% \usepackage{amsthm}
% \usepackage{amssymb}
% \usepackage[most]{tcolorbox}
% \tcbuselibrary{theorems} % \newtcbtheorem を使うために必要


% --- カスタムカラー定義 ---
\definecolor{myblue}{RGB}{0,110,180}
\definecolor{mygreen}{RGB}{0,150,100}
\definecolor{myorange}{RGB}{230,120,20}
\definecolor{mypurple}{RGB}{120, 80, 190}
\definecolor{mycautionred}{RGB}{192,0,0}
\definecolor{mycautionyellow}{RGB}{255,242,204}


% --- 自動採番される環境の定義 ---

% まず「定理」を基準として定義。番号はセクションごとにリセット
\newtcbtheorem[number within=subsection]{mytheorem}{定理}{
  breakable,
  colback=mygreen!5!white,
  colframe=mygreen!75!black,
  colbacktitle=mygreen!75!black,
  coltitle=white,
  fonttitle=\bfseries
}{thm}

% 定義・命題・補題は、「定理」と同じ番号カウンターを共有する
\newtcbtheorem[use counter from=mytheorem]{mydefinition}{定義}{
  breakable,
  colback=myblue!5!white,
  colframe=myblue!75!black,
  colbacktitle=myblue!75!black,
  coltitle=white,
  fonttitle=\bfseries
}{def}

\newtcbtheorem[use counter from=mytheorem]{myproposition}{命題}{
  breakable,
  colback=mypurple!5!white,
  colframe=mypurple!75!black,
  colbacktitle=mypurple!75!black,
  coltitle=white,
  fonttitle=\bfseries
}{prop}

\newtcbtheorem[use counter from=mytheorem]{mylemma}{補題}{
  breakable,
  width=0.9\textwidth,  % 幅を90%に
  center,               % 中央揃え
  colback=mygreen!5!white,
  colframe=mygreen!75!black,
  colbacktitle=mygreen!75!black,
  coltitle=white,
  fonttitle=\bfseries
}{lem}


% --- 手動でタイトルを指定する、または番号なしの環境 ---

% 例題用のスタイル（番号やタイトルは手動で指定）
\newtcolorbox{myexample}[2][]{
  breakable,
  colback=myorange!5!white,
  colframe=myorange!75!black,
  colbacktitle=myorange!75!black,
  coltitle=white,
  fonttitle=\bfseries,
  title={例題: #2},
  #1
}

% 注意書き用のスタイル（タイトルは「注意」で固定、番号なし）
\newtcolorbox{mycaution}[1][]{
  breakable,
  colback=mycautionyellow,
  colframe=mycautionred,
  colbacktitle=mycautionred,
  coltitle=white,
  fonttitle=\bfseries,
  title={注意},
  #1
}


\newcommand{\bb}[1]{\mathbb{#1}}
\newcommand{\mcal}[1]{\mathcal{#1}}
\newcommand{\st}{\quad \text{s.t.} \quad}
\newcommand{\prsp}{(\Omega, \mcal{F}, \bb{P})}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

% --- 段落インデント設定 ---
\setlength{\parindent}{0pt} % デフォルトはインデントなし

\newlength{\manualparindent}
\setlength{\manualparindent}{1\zw} % ← ここが重要（1zw ではなく 1\zw）


\newcommand{\pindent}{\hspace*{\manualparindent}} % 手動で入れるインデント

\title{Introduction to Asset-Lianility Management}
\date{2026/1/1}

\begin{document}
\maketitle

\section{From Asset Management to Asset-Liability Management}
There was a PENSION FUND CRISIS.
The S\&P 500 DB Pension Plans fell enormouls between Dec 1999 and May 2003.
At the Dex 1999, it had a net surplus of \$ 239 billion, and at the end of the period the surplus turned into a net deficit of \$ 252 billion.
It was in the end of Tech bubble. NASDAQ index also declined grately in that period.

The simmilar thing happend again in 2008.

In asset-liability management, the asset value against the liability value matters.
In other words,
\[F_t = \frac{A_t}{L_t}\]
And surplus is given by a difference between assets and liability values:
\[S_t = A_t - L_t\]

\section{Liability hedging portfolios}
The investers concern mainly about an unexpected increase in the present value of thier liabilities.

A possible solution is called Liability-Hedging portfolios(LHR) or Goal-Hedging portfolio.
There should be a certain cashflow that the liability will take, so that we need to try to make the similar cashflow by adjusting our portfolio.

With respect to the goal, a standard vond is not safe because it only makes a temporary huge cashflow in one period and the payoff of the bond change dramatically depending on the other factors.
The portfolio should be like a retirement bond.

In reality, convinient bond which precisely fit the cashflow unlikely to exist so that we use \textbf{Duration Matching}.
Since duration is the figure of sensitivity against inflation or interest rate change

\section{Liability-driven investing (LDI)}
In order to have a better performance, the one have to expose hisself in to the "Risk".
The hedging is the method to control the risk appropriately to prepare for an unexpected shocks.
Performance-seeking portfolio (PSP) and Liability Hedging Portfolio (LHR) are the one of the strategies which try to tame risk.

The optimal allocation strategy is giben by
\[\max_{w} \bb{E}\left[u\left(\frac{A_T}{L_T}\right)\right]\]
\[\therefore w^* = \frac{\lambda_{\text{PSP}}}{\gamma \sigma_{\text{PSP}}}w^{\text{PSP}} + \beta_{\text{L, LHP}}(1- \frac{1}{\gamma})w^{\text{LHP}}\]
where $A_T$ is an asset value, $L_T$ is a liability value and $u$ is an utility function

In the LDI, they also have \textbf{Greeks}
\begin{enumerate}
    \item $\lambda_{\text{PSP}}$ is an sharpe ratio
    \item $\beta_\text{LHP}$ is the beta, sensitivity, of liability
    \item $\sigma_{\text{PSP}}$ is a volatility of the PSP strategy
    \item $\gamma$ is a risk-aversion
\end{enumerate}
\end{document}